---
output: html_document
---
#Telematics Package Examples

This document shows the usage scenarios for the Telematics package. Their are two entry points to using the package.
* 1) If you do not have a Master Summary File created and you want to create One
* 2) If you have a Master Summary File and you want to load it and do some analysis



Defining some variable
```{r}
library(package = "niraj9.telematics")
public.folder = "/home/niraj9/public/"
master.file.3 = paste(public.folder , "master-3.csv" , sep = "")
master.file.4 = paste(public.folder , "master-4.csv" , sep = "")

```

## Scenario 1 - Create a Master Summary File
```{r}
telematics <- Telematics$new(master.file.4)
arun = telematics$CreateMasterSummary(file.list = "/home/niraj9/public/fileList.csv" ,
                                         root.folder = "/home/niraj9/public/drivers/",
                                         subset.driver.count = 30 ,
                                         cores =4)
```


## Scenario 2 - Load an existing Master Summary File

```{r, echo=FALSE}
telematics <- Telematics$new(master.file.3)
telematics$load(verbose = FALSE)
```

## Driver Analysis - Example 1 - Show Drivers loaded

```{r}
telematics$drivers()

```

Load a Driver
```{r}
driver = Driver$new(db = telematics , driver.name = "2751")
driver$summary()
```

## Driver Analysis - Example 2 - Show Driver Graphs

```{r}
q =driver$ShowCoordinates(trip = 165)
q =driver$ShowVelocity(trip = 165)
q =driver$ShowAcceleration(trip = 165)
q =driver$ShowBreaks(trip = 165)
q=driver$ShowQuantiles(trip = 111)
q=driver$ShowSpeedBreaks(trip = 120)

```

## Driver Analysis - Example 3 - Driver Signature Predictive Model
Create a Unique Driver Signature. i.e a GBM Model that can identify a driver
```{r}
model = driver$CreateDriverSignature()
summary(model)

```

## Driver Analysis - Example 4 - Driver Class Predictive Model
Use  the Telematics class to segment the drivers into 5 driver classes
```{r}
fit <- telematics$SegmentDrivers(segments = 5)
summary(fit)

```

Visualize the Driver Clusters
```{r}
telematics$VisualizeSegments()

```


